Crop diversification in a game against nature in a mediterranean agro-ecosystem

### 2020-01-24 risk-percption.Rmd
remove maximax calculation uisng lpsolve

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

maximax
```{r}
risk <- 0.9
wheat_exp <- wheat_wet * (1 - risk) + wheat_dry * risk
barley_exp <- barley_wet * (1 - risk) + barley_dry * risk
obj.fun <- c(wheat_exp, barley_exp)

constr=matrix(c(1,1,1,0,0,1, wheat_exp, barley_exp),ncol = 2, byrow = TRUE) #Loading the constraints
constr.dir=c("=",">=",">=", ">=")
constr.rhs=c(1,0,0, .5)

mod=lp("min",obj.fun,constr,constr.dir,constr.rhs) #Using lp() to solve our problem
mod$solution
```

>>>>

moran_birth_death <- function(agents, r = 1) {
```{r}
load('../Silvanus/R/sysdata.rda')
life_table
fertility_shape <- 4.579627
fertility_scale <- 0.1

die <- function(individuals, food_ratio = 0.7) {
  individuals %>%
        left_join(life_table, by = 'age') %>%

```{r}
reduce(1:600, ~reproduce(.x) %>% die , .init = agents2 %>% mutate(age = sample.int(80, size = 150, replace = TRUE))) %>%
```
